\vspace{-0.25em}\thetitle

### 2009-07-24 paper.tex
...

Our answer to the question of why low-dimensional linear structure appears in the feature-frequency representation of network traffic can be posed in the form of a model.
A mixture model, to be specific.
We propose to view each flow as having a probability distribution of possible behaviors it could exhibit.
% We propose that the behavior of each flow is drawn from a probability distribution on a space possible behaviors.
We hypothesize that the behavior distribution for most flows is a mixture of a relatively small set of ``basic behaviors.''
Moreover, only even smaller subsets of these basic behaviors are ever mixed with each other.

>>>>

Our answer to the question of why low-dimensional linear structure appears in the feature-frequency representation of network traffic can be posed in the form of a model.
% A mixture model, to be specific.
We propose viewing each flow as having a probability distribution of possible behaviors it could exhibit.
% We propose that the behavior of each flow is drawn from a probability distribution on a space possible behaviors.
We hypothesize that the behavior distribution for most flows is a mixture of a relatively small set of ``basic behaviors.''
Moreover, only even smaller subsets of these basic behaviors are ever mixed with each other.
Under these assumptions, we can express the distribution of each flow's behaviors as a finite mixture model~\cite{McLachlan00}:
\begin{align}\eqn{mixture-model}
  q_i(x) = \sum_{j=1}^r w_{ij} p_j(x),
\end{align}
Here $q_i$ and $p_j$ are probability density functions, and $w_{ij}$ are nonnegative weights, summing to unity for each $i$.
